More equivalences for Open pNets\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2019-03-11 2016-Weak-FH-Bisim/WeakBisim.tex
skype Push

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
				{{\Post_p^b}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$

@@

\TODO{A revoir pas correct!: From cases 1, 2 and 3 we have for all $k\in [0\ldots n]$, $\beta_{kj_0}=\alpha_k$. Moreover,} \\

We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}=[\alpha'_0.. \alpha'_n]$, indeed $\displaystyle{\gamma_{j_0}}$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!1)] \land \alpha_p\neq \tau$.
%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

For  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
Therefore, we can conclude that we have for all $k\in [0..n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i),\text{and~}$\\
$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=0}^n
		\Post_p}$  \\
We have:\\
$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}}\big)$\\
By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ by their equivalent formula  we obtain:\\
$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred^{1a}_i}
		\land {\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land}\\
~~\qquad\qquad\qquad({\Pred^{2a}}\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)$\\
By distribution of the substitution operation over the logical operator we can deduce:\\
$\Pred\iff \displaystyle{\big(\bigwedge_{i=0}^{m_1}
{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land} \\
~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land\\	
~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}
$\\		
Therefore, we have:\\
$\Pred\iff \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i)$\\ where $n=m_1+m_2+1$	\\
Concerning the postcondition we have:\\
$\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ we obtain:\\
$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
		{\Post^{3b}_i}} \subst{{\Post^{2a}}\uplus 
		{\Post^{2b}}} \bigotimes_{j=0}^{m_1}\subst{ {\Post^{1a}_i}\uplus 
		{\Post^{1b}_i}}}\\
~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \bigotimes_{i=0}^{m_2}{\Post_i^{3b}}\subst{{\Post^{2b}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1b}}} \\
~~\qquad= \Post' \uplus \bigotimes_{j=0}^{n} \Post_j $\\
 where $n=m_1+m_2+1$	
\end{proof}
\TODO{Pour le post j'ai fait court, je n'ai pas developpe...?}

@@

\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
Also, by Lemma \ref{lem-rel-OT-WOT} this implies the following:\\
$\forall k\! \in\! [0..m']\,\, Q\models{\openrule
			{
				(\beta^1_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_k^{1b}}},  
				{{\Post_k^{1b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{s_{l}^{l\in L_Q}} \OTarrow {\alpha'_p}
				\ostate{s_{l}'^{l\in L_Q}}}
				}%\]
$
and
$\forall k \in [0..n']\,\, Q\models{\openrule
			{
				(\beta^3_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:

\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			\beta_j^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred^2\land\Pred^{2b}\land \alpha'_p=\beta_{j_0},  
			\Post^2\uplus \Post^{2b}}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]

>>>>

$\forall p \in [0..(n_1\!+\!n_2\!+\!2)]\,\, Q\models{\openrule
			{
				(\beta_{pj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^b}},  
				{{\Post_p^b}}}
				{\ostate{v_{pl}^{l\in L_Q}} \OTarrow {\alpha_{p}}
				\ostate{v_{(p+1)l}^{l\in L_Q}}}
				}%\]
$ 
In this equation, and using cases 1, 2 and 3 above, we have for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$.

@@

We have: 
$\displaystyle{\gamma_{j_0}}=\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}}$

Additionally, we have
$[\alpha'_0.. \alpha'_n]$ is a a list of $\alpha_p$ such that $p\in [0..(n_1\!+\!n_2\!+\!2)] \land \alpha_p\neq \tau$ where for all $k\in [0\ldots n_1+n_2+2]$, $\beta_{kj_0}=\alpha_k$. In other words, $\mybigdotcup_{i=0}^{m_1}  \vis{\beta^1_{i{j_0}}} \dotcup  \vis{\set{\beta^2_i}} \dotcup \mybigdotcup_{i=0}^{m_2} \vis{\beta^3_{i{j_0}}} = [\alpha'_0.. \alpha'_n]$. This ensures that $\gamma_{j_0}=[\alpha'_0.. \alpha'_n]$.

%$\displaystyle{\gamma_{kj_0} }=\mybigdotcup_{i=0}^{(n'-1)}\!\!\vis{\beta^1_{ij_0}}\,\dotcup\,\vis{\set{\beta^2_{j_0}}}\,\dotcup\!\!\!\mybigdotcup_{i=(n'+1)}^{(n_k-1)}\!\!\!\vis{\beta^3_{ij_0}}$ \TODO{?????}\\

Consequently, for  $\gamma_{j_0}=[\beta_0..\beta_n]$ such that $\beta_i=\alpha'_i$ we have $n$ weak open transitions  $\symb{WOT}_k$ such that $k\in [0..n]$.
Therefore, we can conclude that we have for all $k\in [0..n]$:  
\begin{mathpar}
Q\models{\openrule
			{
			\gamma_{kj}^{j\in J_k}, {\Pred_k}, {\Post_k}}
			{\ostate{s_{pl}^{l\in L_Q}} \OTWeakarrow {\alpha_{k}}
				\ostate{s_{(p+1)l}^{l\in L_Q}}}
		}%\]
\end{mathpar}
and $\displaystyle{\bigcup_{p=0}^nJ_{p}} = J\cap\Holes(Q)$, $\forall j\in J_p,\,\gamma_j= \displaystyle{\mybigdotcup_{p=0}^n \gamma_{p j}}$, $\forall l\in L_Q,\, s_{0l}=s_l$, $s_{(n+1)l}=s'_l$  \\
  $\Pred \iff \Pred\,'
		\land \displaystyle{\bigwedge_{p=0}^n}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i),\text{and~}$\\
$\displaystyle{\Post=\Post\,'\uplus\bigotimes_{p=0}^n
		\Post_p}$  \\
We have:\\
$\Pred=\displaystyle{\bigwedge_{i=0}^{m_1}\!\big(\Pred^1_i\bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land\Pred^2\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land \bigwedge_{i=0}^{m_2}\!\Pred_i^3\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}}\big)$\\
By replacing ${\Pred^{1}_i}$,  $\Pred^2$, and ${\Pred^{3}_i}$ by their equivalent formula  we obtain:\\
$\Pred \iff\displaystyle{\bigwedge_{i=0}^{m_1}({\Pred^{1a}_i}
		\land {\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\big)\land}\\
~~\qquad\qquad\qquad({\Pred^{2a}}\land {\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
~~\qquad\qquad\bigwedge_{i=0}^{m_2} ({\Pred^{3a}_i}\land {\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\big(\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\big)$\\
By distribution of the substitution operation over the logical operator we can deduce:\\
$\Pred\iff \displaystyle{\big(\bigwedge_{i=0}^{m_1}
{\Pred_i^{1a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{1a}}}\big)
\land{\Pred^{2a}}\bigotimes_{i=0}^{m_1}\subst{{\Post_i^{1a}}}\land} \\
~~\qquad\qquad\quad\big(\bigwedge_{i=0}^{m_2}{\Pred_i^{3a}}\bigotimes_{j=0}^{i-1}\subst{{\Post_j^{3a}}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}}\big) \land\\	
~\qquad\qquad\quad\bigwedge_{i=0}^{m_1}({\Pred^{1b}_i}\land \alpha^1_i=\beta^1_{ij_0}) \bigotimes_{j=0}^{i-1}\subst{\Post_j^1}\land({\Pred^{2b}}\land \alpha^2=\beta^2_{j_0})	\bigotimes_{i=0}^{m_1}\subst{\Post_i^1}\land\\
~\qquad\qquad\quad\bigwedge_{i=0}^{m_2} ({\Pred^{3b}_i}\land \alpha^3_i=\beta^3_{ij_0})\bigotimes_{j=0}^{i-1}\subst{\Post^3_j}\subst{\Post^2}  \bigotimes_{i=0}^{m_1}\subst{\Post_i^1}
$\\		
Therefore, we have:\\
$\Pred\iff \Pred\,' \wedge \displaystyle{\bigwedge_{p=0}^{n}}((\alpha_p= \beta_{pj_0}\land \Pred_p)\bigotimes_{i=0}^{p-1}\Post_i)$\\ where $n=m_1+m_2+1$	\\
Concerning the postcondition we have:\\
$\Post=\displaystyle{\bigotimes_{i=0}^{m_2}\Post^3_i\subst{\Post^2}\bigotimes_{j=0}^{m_1}\subst{\Post^1_j}}$\\
By replacing ${\Post^{1}_i}$,  $\Post^2$, and ${\Post^{3}_j}$ and because the ${\Post_i^{ja}}$ and ${\Post_i^{jb}}$ are independent (the ${\Post_i^{ja}}$ concern the leaves of $P$ while the ${\Post_i^{jb}}$ concern the leaves of $Q$), we obtain:\\
$\Post= \displaystyle{\bigotimes_{i=0}^{m_2}\subst{{\Post^{3a}_i}\uplus 
		{\Post^{3b}_i}} \subst{{\Post^{2a}}\uplus 
		{\Post^{2b}}} \bigotimes_{j=0}^{m_1}\subst{ {\Post^{1a}_i}\uplus 
		{\Post^{1b}_i}}}\\
~~\qquad= \bigotimes_{i=0}^{m_2}{\Post_i^{3a}}\subst{{\Post^{2a}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1a}}} \uplus \bigotimes_{i=0}^{m_2}{\Post_i^{3b}}\subst{{\Post^{2b}}}\bigotimes_{j=0}^{m_1}\subst{{\Post_j^{1b}}} \\
~~\qquad= \Post' \uplus \bigotimes_{j=0}^{n} \Post_j $\\
 where $n=m_1+m_2+1$	
\end{proof}

@@

\begin{mathpar}
Q\models{\openrule
	{
		\gamma_{p j}^{j\in J_p},
		 \Pred_p,  
		\Post_p}
	{\ostate{s_{p i}^{i\in L_Q}} \OTWeakarrow {\alpha_p}
		\ostate{s_{(p+1) i}^{\, i\in L_Q}}}
}		
\end{mathpar}
Also, by Lemma \ref{lem-rel-OT-WOT} this implies the following:\\
$\forall k\! \in\! [0..m']\,\, Q\models{\openrule
			{
				(\beta^1_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_k^{1b}}},  
				{{\Post_k^{1b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
,$ 
$Q\models{\openrule
			{
				(\beta^2_j)^{j\in J\cap\Holes(Q)}, {{\Pred^{2b}}},  
				{{\Post^{2b}}}}
				{\ostate{s_{l}^{l\in L_Q}} \OTarrow {\alpha'_p}
				\ostate{s_{l}'^{l\in L_Q}}}
				}%\]
$
and
$\forall k \in [0..n']\,\, Q\models{\openrule
			{
				(\beta^3_{kj})^{j\in J\cap\Holes(Q)}, {{\Pred_p^{3b}}},  
				{{\Post_p^{3b}}}}
				{\ostate{s_{kl}^{l\in L_Q}} \OTarrow {\tau}
				\ostate{s_{(k+1)l}^{l\in L_Q}}}
				}%\]
$\\ 
Knowing that we have $j_0\in J$ and $\gamma_{j_0}=[\beta_0..\beta_n]$:
Suppose that $Q$ moves in transition $\alpha$, then there is  a matching $p_0$ transition for some $p_0\in[0..n]$. 
\[ P[Q]_{j_0}  
	\models
	{\openrule
		{
			(\beta^2_j)^{(j\in J\setminus\{j_0\}) \uplus J_Q}, 
			\Pred^2\land\Pred^{2b}\land \alpha'_{p_0}=\beta^2_{j_0},  
			\Post^2\uplus \Post^{2b}}
		{\ostate{s_i^{i\in L\uplus L_Q}} \OTarrow {\alpha}
			\ostate{s_i'^{\, i\in L\uplus L_Q}}}
	}
	\]
NOTE: And $\beta^2_{j_0}= \beta_{p_0}$.
